Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-18 cav2017/cav2017.tex
minor change

For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\ref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}. Thus, the states are computed using the following equations:
\begin{equation}
\label{eq:ssunroll}
\left\lbrace
\begin{array}{l}
u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
x_{k+1}=Ax_{k}+Bu_{k}
\end{array}\right.
\end{equation}

>>>>

For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\eqref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}. Thus, the states are computed using the following equations:
\begin{equation}
\label{eq:ssunroll}
\left\lbrace
\begin{array}{l}
u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
x_{k+1}=Ax_{k}+Bu_{k}
\end{array}\right.
\end{equation}
